`phyr`: An R package for model-based phylogenetic analyses

### 2018-11-02 ms.Rmd
update pglmm [skip ci]

---
title: "`phyr`: An R package for model-based phylogenetic analyses"
author: "Daijiang Li, Russell Dinnage, Lucas Nell, Anthony Ives"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::html_document2:
    number_sections: no
    theme: sandstone
    toc: yes
    css: style.css
  bookdown::word_document2: 
    toc: no
  bookdown::tufte_html2:
    number_sections: no
    toc: yes
fontsize: 12pt
link-citations: yes
csl: https://raw.githubusercontent.com/citation-style-language/styles/master/methods-in-ecology-and-evolution.csl
bibliography: ref.bib
---

@@

Then brief introduction of each topic

@@

`communityPGLMM` or `pglmm`

>>>>

---
title: "`phyr`: An R package for model-based phylogenetic analyses"
author: "Daijiang Li, Russell Dinnage, Lucas Nell, Anthony Ives"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::html_document2:
    number_sections: no
    theme: sandstone
    toc: yes
    css: style.css
  bookdown::word_document2: 
    toc: no
  bookdown::tufte_html2:
    number_sections: no
    toc: yes
fontsize: 12pt
link-citations: yes
always_allow_html: yes
csl: https://raw.githubusercontent.com/citation-style-language/styles/master/methods-in-ecology-and-evolution.csl
bibliography: ref.bib
---

@@

@@

The original code for `communityPGLMM` were imported from the R package `pez` [@pearse2015pez]. Its theorectical background was presented in @ives2011generalized. We improved both the user interface and the speed of `communityPGLMM` here. Function `pez::communityPGLMM` requires user-prepared random terms while `phyr::communityPGLMM` makes this step much easier by adapting formula syntax for mixed models provided by the R package `lme4` [@bates2015lme4].
